\mytitle

### 2020-04-29 paper.tex
Added comment on the approximations.
Finished edit of Section 2

In our work, we build upon the approach in Donovan~\cite{donovan2005wind}, yet instead of using a linear version of the LS objective, we 
model WFLO using a quadratic representation. %The difference between our approach and the quadratic model
%proposed in
Unlike Turner et al.\ \cite{turner2014new} and Ulku and Alabas-Uslu\ \cite{ulku2019new}, our model is not an approximation of the SS objective, 
but an rather an exact representation of the LS objective.

While the main advantage of exact techniques
is that they provide guarantees on solution quality, they may take a very long time to  find an optimal solution. 
In fact, Section~\ref{sec:QUBO4WFLO} shows that WFLO is computationally hard, a result
that we have not yet encountered in the WFLO literature. Therefore,
when one considers solving multiple wind farm design problems, a fast solution is of essence,
and hence one may turn to approximate WFLO.

\paragraph{Approximate Methods} In contrast to exact methods, approximation algorithms often provide   
quick and, hopefully, sufficiently accurate solutions. Several works solved 
WFLO using evolutionary (genetic) approaches~\cite{MOSETTI1994105,gonzalez2010optimization,grady2005placement}. 
These methods use two principles (cross-over and mutation)
to change existing solutions and improve them over time. Evolutionary methods do not guarantee termination 
(i.e., they may run forever without achieving a quality criteria), and even when they do terminate (in practical cases) they do
not guarantee optimal solutions. Hence, one must often
introduce non-quality related stopping criteria, 
thus compromising on the quality of the obtained solution~\cite{davis1991handbook}.
Furthermore, there is no natural way of introducing constraints into genetic methods, which
leads to a potentially costly feasibility check for every solution found.

The first attempt to address these limitations 
was made using a local search approach for WFLO~\cite{ozturk2004heuristic}. 
The solution does not guarantee optimality, 
yet it circumvents the termination and feasibility checking issues of the evolutionary
methods. The local search approach attempts to apply either move, remove or add actions given an incumbent 
feasible solution. When a turbine is moved, removed or added, the new solution is evaluated. The procedure terminates 
when a stopping criteria is reached.
The main limitation of this approach 
%~\cite{ozturk2004heuristic}
is that it cannot perform an action 
that leads to an infeasible state and, therefore, quickly converges to a sub-optimal solution (local optimum) 
that can potentially be much lower quality than the globally optimal solution~\cite{rivas2009solving}.

To overcome this limitation, Rivas et al.\ \cite{rivas2009solving} used simulated annealing (SA), 
a neighborhood search method that allows visits to infeasible solutions. 
This creates a well-connected solution space that leads the algorithm to escape 
local optima. The SA method was shown to be superior to Ozturk \& Norman~\cite{ozturk2004heuristic} 
and to the genetic method proposed in Grady et al.\ \cite{grady2005placement}. A drawback of the SA approach 
is its ad-hoc nature. The various components of the algorithm
 must be tailored to the problem at hand and, as a result, small adjustments of the WFLO setting
 (e.g., adding noise considerations), would require major changes to the SA implementation. 
Additional methods and experimental comparisons between various approximate algorithms are available in Samorani~\cite{samorani2013wind}.

In our work, we also use an SA approach (similarly to Rivas et al.\ \cite{rivas2009solving}). However,
our methodology is generic since it is based on a declarative problem model and
on the ability of specialized hardware to solve (non-ad-hoc) quadratic problems.

>>>>

In our work, we build upon the approach in Donovan~\cite{donovan2005wind}, yet instead of using a linear version of the LS objective, we 
model WFLO using a quadratic representation. %The difference between our approach and the quadratic model
%proposed in
Unlike Turner et al.\ \cite{turner2014new} and Ulku and Alabas-Uslu\ \cite{ulku2019new}, our model is not an approximation of the SS objective, 
but rather an exact representation of the LS objective. That is, while the previous work has approximated a more accurate physical model, we are exactly representing the less accurate physical model: the approximation arises at a different stage of the modeling pipeline.

While the main advantage of exact techniques
is that they provide guarantees on solution quality, they may take a very long time to  find an optimal solution. 
In fact, Section~\ref{sec:QUBO4WFLO} shows formally that WFLO is computationally hard, a result
that we have not yet encountered in the WFLO literature. Therefore,
when one considers solving multiple wind farm design problems, if a fast solution is of essence,
one may turn to approximate optimization techniques.

\paragraph{Approximate Methods} In contrast to exact methods, approximation algorithms often provide   
quick and, hopefully, sufficiently accurate solutions. Several works have solved 
WFLO using evolutionary (genetic) approaches~\cite{MOSETTI1994105,gonzalez2010optimization,grady2005placement}. 
%These methods use two principles (cross-over and mutation)
%to change existing solutions and improve them over time.
These methods do not guarantee termination 
(i.e., they may run forever without achieving a quality criteria), and even when they do terminate (in practical cases) they do
not guarantee optimal solutions. Hence, one must often
introduce non-quality related stopping criteria, 
thus compromising on the quality of the obtained solution~\cite{davis1991handbook}.
Furthermore, there is no natural way of introducing constraints into genetic methods (see e.g., \cite{sorkhabi2018constrained}), which
leads to a potentially costly feasibility check for every solution found.

The first attempt to address these limitations 
was made using a local search approach~\cite{ozturk2004heuristic}. 
The solution does not guarantee optimality, 
yet it circumvents the termination and feasibility checking issues of the evolutionary
methods. The local search approach attempts to apply either move, remove or add actions given an incumbent 
feasible solution. When a turbine is moved, removed or added, the new solution is evaluated. The procedure terminates 
when a stopping criteria is reached.
The main limitation of this approach 
%~\cite{ozturk2004heuristic}
is that it cannot perform an action 
that leads to an infeasible state and, therefore, often quickly converges to a sub-optimal solution (local optimum) 
that can potentially be much lower quality than the globally optimal solution~\cite{rivas2009solving}.

To overcome this limitation, Rivas et al.\ \cite{rivas2009solving} used simulated annealing (SA), 
a neighborhood search method that allows visits to infeasible solutions. 
This creates a well-connected solution space that leads the algorithm to escape 
local optima. The SA method was shown to be superior to the approach of Ozturk \& Norman~\cite{ozturk2004heuristic} 
and to the genetic method proposed in Grady et al.\ \cite{grady2005placement}. A drawback of the SA approach 
is its ad-hoc nature. The various components of the algorithm
 must be tailored to the problem at hand and, as a result, small adjustments of the WFLO setting
 (e.g., adding noise considerations), would require major changes to the SA implementation. 
Additional methods and experimental comparisons between various approximate algorithms are available in Samorani~\cite{samorani2013wind}.

In our work, we also use an annealing based approach (similar to Rivas et al.\ \cite{rivas2009solving}). However,
our methodology is generic since it is based on a declarative problem model and
on the ability of specialized hardware to solve (non-ad-hoc) quadratic problems.
